### 2015-04-17 abstract2.tex
盲审版本

%\thispagestyle{empty} %取消当前页码
%\chapter[ABSTRACT（英文摘要）]{Abstract}
\begin{tabular}{l l}
Title：& Research on Proper Loops in Answer Set Program\\
Major：& Software Engineering\\
Name：& Zhenfeng Yuan\\
Supervisor：& Hai Wan\\
\end{tabular}
\vspace{0.5cm}
%\chapter*{Abstract}
% \markboth{英~文~摘~要}{英~文~摘~要}
\phantomsection
\addcontentsline{toc}{chapter}{Abstract}

@@

{\bf Key Words:  ASP solver, normal logic programs, disjunctive logic programs, loop formulas, elementary loops, proper loops}
%\clearpage

>>>>

%\thispagestyle{empty} %取消当前页码
%\chapter[ABSTRACT（英文摘要）]{Abstract}
%\begin{tabular}{l l}
%Title：& Research on Proper Loops in Answer Set Program\\
%Major：& Software Engineering\\
%Name：& Zhenfeng Yuan\\
%Supervisor：& Hai Wan\\
%\end{tabular}
%\vspace{0.5cm}
%\chapter*{Abstract}
% \markboth{英~文~摘~要}{英~文~摘~要}
\phantomsection
\addcontentsline{toc}{chapter}{Abstract}

@@

{\bf Key Words: normal logic programs, disjunctive logic programs, loop formulas, elementary loops, proper loops, ASP solver}
%\clearpage
